---
title: "SMI-FinalProj-TruthSocialAnalysis"
author: "Joseph"
date: "4/15/2023"
output: html_document
---

```{r setup, include=FALSE}
# Specify the chunks you DON'T want to be knitted to the file: "{r, include=FALSE}"
# If you are knitting, and wants to insert a new line, be sure to add 2 whitespaces at the end in the text.  
knitr::opts_chunk$set(echo = TRUE)
getwd() # check working directory. (should be the same as .Rproj)
rm(list=ls()) # remove unwanted data
```

**install / load packages**  
reference: https://statsandr.com/blog/an-efficient-way-to-install-and-load-r-packages/
```{r, include=TRUE}
# Install "pacman" package for "p_load" function if not yet installed
pacman_installed <- "pacman" %in% rownames(installed.packages())
if (pacman_installed == FALSE) {
  install.packages("pacman")
}
rm(pacman_installed)
```

**Remove Dummy Variables at Once**  
Better to create dummy variables with tmp.xxx, or xxx.tmp, and remove them all at once.  
You'll be able to do that with this function remove_tmp().  
```{r}
remove_tmp <- function(){
  rm(list = ls(pattern = "^tmp[.]", envir = .GlobalEnv), envir = .GlobalEnv)
  rm(list = ls(pattern = "[.]tmp$", envir = .GlobalEnv), envir = .GlobalEnv)
}
```

```{r}
# load the packages you need
pacman::p_load(tidyverse, modeest, Rmisc, dplyr, ggplot2, readr)
```

**load the dataset**
```{r}
DATA_PATH <- "..\\Dataset\\truth_social"
load_tsv <- function(filename){
  return(read_tsv(file.path(DATA_PATH, filename)))
}
```

```{r}
df.users<-load_tsv("users.tsv")
df.truths<-load_tsv("truths.tsv")
df.hashtags<-load_tsv("hashtags.tsv")
df.truthHashTagEdges<-load_tsv("truth_hashtag_edges.tsv")
df.truthUserTagEdges<-load_tsv("truth_user_tag_edges.tsv")
df.follows<-load_tsv("follows.tsv")
```

```{r}
summary(df.truthHashTagEdges)
summary(df.hashtags)
```

What are the most common #hashtags? grouped bar chart
**Top 20 hashtags barchart: **
1. create frequency data and extract top 20
```{r}
# groupby df.truthHashTagEdges.hashtag_id, count rows of df.truthHashTagEdges, get top20 counts hashtag_id, count
df.agg.top20hashtags <- df.truthHashTagEdges %>%
  group_by(hashtag_id) %>%
  dplyr::summarize(cnt = n()) %>%
  arrange(desc(cnt), .by_group = TRUE) %>%
  slice(1:20)
df.agg.top20hashtags
```

```{r}
head(df.hashtags, n=10)
```

2. add bin information: link label text df.hashtags.hashtag to df.truthHashTagEdges.hashtag_id
```{r}
df.agg.top20hashtags <- df.agg.top20hashtags %>%
  inner_join(df.hashtags, by = c('hashtag_id'='id')) %>%
  select(hashtag_id, hashtag, cnt)
df.agg.top20hashtags
```

3. plot top 20 hashtags barchart
```{r}
# The reorder method: 
graph.top20hashtags <- ggplot(df.agg.top20hashtags, aes(x=reorder(hashtag, +cnt), y=cnt)) +
  geom_bar(stat = 'identity', wide=0.2) +
  labs(title="Top 20 hashtags", x="hashtag", y="count") +
  coord_flip()
graph.top20hashtags


# # The factor method: tell ggplot afterwards that I have an order factor already
# df.agg.top20hashtags$hashtag2 <- factor(df.agg.top20hashtags$hashtag, levels = df.agg.top20hashtags$hashtag[order(df.agg.top20hashtags$cnt, decreasing = FALSE)])
# df.agg.top20hashtags
# graph.top20hashtags <- ggplot(df.agg.top20hashtags, aes(x=hashtag2, y=cnt)) +
#   geom_bar(stat = 'identity', wide=0.2) +
#   coord_flip()
# graph.top20hashtags
```


**Top Retruthed Users Barchart: **
```{r}
# df.agg.originaltruths <- df.truths[!df.truths$is_retruth & !df.truths$is_reply, ]
# df.agg.originaltruths # 317706 obs.
# 
# df.agg.originaltruths2 <- df.truths[df.truths$truth_retruthed==-1, ]
# df.agg.originaltruths2 # 600864 obs.
# 
# df.agg.originaltruths3 <- df.truths[!df.truths$is_retruth & !df.truths$is_reply & df.truths$truth_retruthed==-1, ]
# df.agg.originaltruths3 # 317704 obs.

# # only 2 obs. are !(!is_retruth & !is_reply & truth_retruthed!=-1)
# tmp.0 <- df.agg.originaltruths %>%
#   anti_join(df.agg.originaltruths3, by = "id")

# id=813604 --> !is_retruth & !is_reply & truth_retruthed=1058980
# id=898948 --> !is_retruth & !is_reply & truth_retruthed=896021
# Mostly True that !df.truths$is_retruth & !df.truths$is_reply is a subset of df.truths$truth_retruthed==-1
# Suspicious that some of the df.truths$truth_retruthed==-1 represents missing data. 
# ...or it means quote? quotes only have 10508 entries.
# use !df.truths$is_retruth & !df.truths$is_reply & df.truths$truth_retruthed==-1 as Original Truth. 

df.agg.originaltruths <- df.truths[!df.truths$is_retruth & !df.truths$is_reply & df.truths$truth_retruthed==-1, ]
df.agg.originaltruths # 317704 obs.

# Top 20 (also try Top 10000) retruthed original truths

# Nodes: the retruths that retruthed original_truths
# Author = Source's author id, Source = retruth/reply id, Target = original truth id
df.nw.AuthorNetwork <- df.truths %>%
  semi_join(df.agg.originaltruths, by = c('truth_retruthed'='id')) %>%
  select(Author = author, Source = id, Target = truth_retruthed)
df.nw.AuthorNetwork

df.agg.topN_retruthed_Truths <- df.nw.AuthorNetwork %>%
  group_by(Target) %>%
  dplyr::summarize(retruthed_cnt = n()) %>%
  arrange(desc(retruthed_cnt)) %>%
  slice(1:100000)
# df.agg.topN_retruthed_Truths

df.agg.topN_retruthed_Author <- df.agg.topN_retruthed_Truths %>%
  inner_join(df.truths, by = c('Target'='id')) %>%
  select(orig_truth_id=Target, orig_truth_author=author, retruthed_cnt) %>%
  inner_join(df.users, by = c('orig_truth_author'='id')) %>%
  select(orig_truth_id, orig_truth_author, username, retruthed_cnt) %>%
  group_by(orig_truth_author, username) %>%
  dplyr::summarize(total_retruthed_cnt = sum(retruthed_cnt)) %>%
  arrange(desc(total_retruthed_cnt))
  # top_n(100)
# weird that slice_max and top_n both are acting weird......
df.agg.topN_retruthed_Author<-df.agg.topN_retruthed_Author[1:20,]
df.agg.topN_retruthed_Author


graph.topN_retruthed_Author <- ggplot(df.agg.topN_retruthed_Author, aes(x=reorder(username, +total_retruthed_cnt), y=total_retruthed_cnt)) +
  geom_bar(stat = 'identity', wide=0.2) +
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12)) +
  labs(title="Top N Retruthed Users", x="username", y="total retruth count") +
  coord_flip()
graph.topN_retruthed_Author


```


- top 20 retruthed authors top 10 hashtags --> real total hashtag frequency bar chart
```{r}

```


We should be concerned about the collection bias of this dataset. 
Author claims that network average path length is short, and post content is diverse, which should be some proof that the dataset represents Truth Social enough. 
-> Watts and Strogatz model random network? BA model scale-free networks? they all predicted very short average path length! 
-> Real Network: high cluster coefficient + short avg path length + high sparsity







**Network Analysis**
- followers distribution
- follows.tsv network (4,002,115 #records, becareful)
- Top 20 followed bar chart

- Author/User Network
  Dataset: truths.tsv
  node: author, edge: id, Source=retruth author/user, Target=truth_retruthed author/user
  edge size coded: freq of (source, target)
  ...Too many user nodes. Partition. 
  ...Can we get In-Degree Distribution plot faster than constructing a network graph? If so, observe the In-Degree Distribution first. 
    -> plot top 10000 retruth histogram
  ...Minimized Author Network: Top 1000 retruthed Authors + Top 500000 retruthing Authors
  ...
  ...Or, first filter out 'Original Truths' using !is_retruth & !is_reply
  

**Create NetworkData for Gephi**
follows network graph
```{r}
head(df.follows)
```

```{r}
df.nw.follows <- df.follows %>%
  select(id, time_scraped, Source=follower, Target=followed) %>%
  inner_join(df.users, by=c('Source'='id')) %>%
  select(id, time_scraped.x, Source, src_username = username, Target) %>%
  inner_join(df.users, by=c('Target'='id')) %>%
  select(id, time_scraped.x, Source, src_username, Target, tar_username = username)
head(df.nw.follows)

write_tsv(df.nw.follows, file.path(DATA_PATH, "follows_nwgraph.tsv"))
```



























